Reduced plasticity and opportunity for selection in terrestrial ectotherm populations

### 2023-04-12 ms.qmd
Not comfrotable with smoothers and don't seem to work with many brms functions to check. Simplifying model to linear and interaction between lata nd long separetd by habitat

   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + habitat + type + type:habitat + t2(long.x, lat.y, by = habitat) + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)

@@

pred <- conditional_smooths(model5_bayes)
pp_check(model5_bayes)
```

>>>>

   model5_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type*habitat + long.x*lat.y*habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_wild_cvr)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_wild_cvr=A_wild_cvr), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.99, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data_wild)

@@

pred <- conditional_effects(model5_bayes)
pp_check(model5_bayes)
```
